Synthesizing Quotient Lenses

### 2018-02-20 papers/QuotientLenses/main.tex
edits to sec 2

\section{Quotient Regular Expressions and Lenses by Example}
\label{sec:example}
In this section, we explain the difficulties of programming with quotient lenses
in Boomerang and show, by way of example, how our novel language of {\em
Quotient Regular Expressions}, or QREs, and QRE lenses address these
difficulties.

Consider a bidirectional transformation that converts citation records such as
\begin{verbatim}
@Book {conway,
Author = "J. H. Conway",
Title = {Regular Algebra and Finite Machines}
}
\end{verbatim}

\noindent stored in the \bibtex{} format to their equivalent representation
\begin{verbatim}
%0 Book
%T Regular Algebra and Finite Machines
%A J. H. Conway
%F conway
\end{verbatim}

\noindent in the EndNote format, and vice versa.

If two \bibtex{} files differ in only ``inessential'' details, we would like
these files to map to the same EndNote representations.
First, the transformation should allow whitespace characters to occur
arbitrarily between the words in the label, author, and title fields, as well as
in between them. Second, an author's name can have the surname followed by a
comma and then the other names separated by arbitrary whitespace, or just all
the names separated by arbitrary whitespace (for example, the names ``Conway, J.
H.'' and ``J. H. Conway'' are equivalent). Lastly, the transformation should
also ignore the order in which the author and title fields occur in each
citation record.

For example, the desired transformation should map the following
\bibtex{} citations to the same EndNote record in the forward direction:
\begin{verbatim}
@Book {conway,
Author = "J. H. Conway",
Title = {Regular Algebra and Finite Machines},
}

>>>>

\section{Quotient Regular Expressions and Lenses by Example}
\label{sec:example}

%In this section, we explain the difficulties of programming with quotient
%lenses in Boomerang and show, by way of example, how our 
%{\em Quotient Regular Expressions} (QREs) help alleviate these difficulties.

Consider a bidirectional transformation that converts
\bibtex{} citation records such as
\begin{verbatim}
@Book {conway,
Author = "J. H. Conway",
Title = {Regular Algebra and Finite Machines}
}
\end{verbatim}
\noindent
to an equivalent EndNote format like the following
\begin{verbatim}
%0 Book
%T Regular Algebra and Finite Machines
%A J. H. Conway
%F conway
\end{verbatim}
\noindent
and vice versa.
%
Transformations from one such representation to the other will preserve
most of the information content of the data:  the title, the author,
and the key, for instance.  However, intuitively,
some of the information is inessential and may be discarded---indeed, this
inessential information will likely appear so trivial that a casual
reader may not even realize it is there to begin with.  For instance,
there is no need to preserve the amount of whitespace between words, at the ends of lines, or
between fields.  In addition, the order of author and title fields is irrelevant.
There may also be additional equivalent ways of writing the same
name:  ``Conway, J. H.'' and ``J. H. Conway'' should probably be treated
the same.

%% Moreover,
%% if two \bibtex{} files differ only in ``inessential'' details, we would like
%% to treat them the same by mapping them to identical EndNote representations.
%% In this , the transformation should allow whitespace characters to occur
%% arbitrarily between the words in the label, author, and title fields, as well as
%% in between them. Second, an author's name can have the surname followed by a
%% comma and then the other names separated by arbitrary whitespace, or just all
%% the names separated by arbitrary whitespace (for example, the names ``Conway, J.
%% H.'' and ``J. H. Conway'' are equivalent). Lastly, the transformation should
%% also ignore the order in which the author and title fields occur in each
%% citation record.

When two instances of the same format differ only terms of such inessential
information, it is often useful to treat them as identical.
For example, the following two
\bibtex{} citations represent the same logical object and as a result, should
be translated to the same EndNote record.
\begin{verbatim}
@Book {conway,
Author = "J. H. Conway",
Title = {Regular Algebra and Finite Machines},
}
